A demonstration of the \LaTeX\ class file for Wiley NJD Journals\protect\thanks{This is an example for title footnote.}

### 2021-09-07 notes.tex

To simplify the problem, suppose there is only one sampling unit, and let $X_1=X$ and $n_1=n$, etc. Then $\beta = \theta_1^*=\theta^*$.
Further assume that $\phi_p$ and $\phi_n$ are known. Let $Y_1,\ldots,Y_n$ be the result of the assay from the $n$ individuals in the population
($Y_i=1$ is positive and $Y_i=0$ is negative). Let $Y_1^*,\ldots,Y_n^*$ be the true disease status ($Y_i^*=1$ is diseased, and $Y_i^*=0$ is not diseased).
Then using the definition of sensitivity and specificity, we get:
\begin{eqnarray*}
Pr[ Y_i =1 | Y_i^*=1] & = & \phi_p \\
Pr[ Y_i=0 | Y_i^*=0] & = & 1- \phi_n
\end{eqnarray*}
and
\begin{eqnarray*}
Pr[ Y_i=1] & = & Pr[ Y_i =1 | Y_i^*=1]  Pr[Y_i^*=1] + Pr[ Y_i =1 | Y_i^*=0] Pr[ Y_i^*=0] \\
& = & \phi_p \theta^* + \phi_n (1-\theta^*)  \\
& = & \theta^* (\phi_p - \phi_n) + \phi_n.
\end{eqnarray*}
Let $\theta = Pr[ Y_i=1]$.

@@

\begin{landscape}
\includepdf[angle=90]{coverage_50}
\end{landscape}

\begin{landscape}
\includepdf[angle=90]{coverage_8000}
\end{landscape}

\begin{landscape}
\includepdf[angle=90]{upper_error_frequency_50}
\end{landscape}

\begin{landscape}
\includepdf[angle=90]{upper_error_frequency_8000}
\end{landscape}

\begin{landscape}
\includepdf[angle=90]{lower_error_frequency_50}
\end{landscape}

\begin{landscape}
\includepdf[angle=90]{lower_error_frequency_8000}
\end{landscape}

@@

>>>>

To simplify the problem, suppose there is only one sampling unit, and let $X_1=X$ and $n_1=n$, etc. Then $\beta = \theta_1^*=\theta^*$.
Further assume that $\phi_p$ and $\phi_n$ are known. Let $Y_1,\ldots,Y_n$ be the result of the assay from the $n$ individuals in the population
($Y_i=1$ is positive and $Y_i=0$ is negative). Let $Y_1^*,\ldots,Y_n^*$ be the true disease status ($Y_i^*=1$ is diseased, and $Y_i^*=0$ is not diseased).
Then using the definition of sensitivity and specificity, we get:
\begin{eqnarray*}Hi M
Pr[ Y_i =1 | Y_i^*=1] & = & \phi_p \\
Pr[ Y_i=0 | Y_i^*=0] & = & 1- \phi_n
\end{eqnarray*}
and
\begin{eqnarray*}
Pr[ Y_i=1] & = & Pr[ Y_i =1 | Y_i^*=1]  Pr[Y_i^*=1] + Pr[ Y_i =1 | Y_i^*=0] Pr[ Y_i^*=0] \\
& = & \phi_p \theta^* + \phi_n (1-\theta^*)  \\
& = & \theta^* (\phi_p - \phi_n) + \phi_n.
\end{eqnarray*}
Let $\theta = Pr[ Y_i=1]$.

@@

% \begin{landscape}
% \includepdf[angle=90]{coverage_50_0_005}
% \includepdf[angle=90]{coverage_8000_0_005}
% \includepdf[angle=90]{coverage_50_0_05}
% \includepdf[angle=90]{coverage_8000_0_05}

% \includepdf[angle=90]{upper_error_frequency_50_0_005}
% \includepdf[angle=90]{upper_error_frequency_8000_0_005}
% \includepdf[angle=90]{upper_error_frequency_50_0_05}
% \includepdf[angle=90]{upper_error_frequency_8000_0_05}

% \includepdf[angle=90]{lower_error_frequency_50_0_005}
% \includepdf[angle=90]{lower_error_frequency_8000_0_005}
% \includepdf[angle=90]{lower_error_frequency_50_0_05}
% \includepdf[angle=90]{lower_error_frequency_8000_0_05}
% \end{landscape}

% \begin{landscape}
% \includepdf[angle=90]{coverage_8000}
% \end{landscape}

% \begin{landscape}
% \includepdf[angle=90]{upper_error_frequency_50}
% \end{landscape}

% \begin{landscape}
% \includepdf[angle=90]{upper_error_frequency_8000}
% \end{landscape}

% \begin{landscape}
% \includepdf[angle=90]{lower_error_frequency_50}
% \end{landscape}

% \begin{landscape}
% \includepdf[angle=90]{lower_error_frequency_8000}
% \end{landscape}

@@

\subsubsection{Damon's Response to 6.3}

First, some notation corrections / clarifications:

Because ${\beta}_a = \sum_{i=1}^{k} w_i \theta_i$, we should let $\hat{\beta}_a= \sum_{i=1}^{k} w_i \frac{X_i}{n_i}$.

Because \( X_i \sim Binomial(n_i, \theta_i )\), we have:

\begin{align*}
	        &   \Var \left( \hat{\beta}_a \right)   =  \Var \left( \sum_{i=1}^k w_i \frac{X_i}{n_i}\right)\\
	\implies&   \Var \left( \hat{\beta}_a \right)   =  \sum_{i=1}^k \left( \frac{w_i}{n_i} \right)^2 \Var X_i \\
	\implies&   \Var \left( \hat{\beta}_a \right)   =  \sum_{i=1}^k \left( \frac{w_i}{n_i} \right)^2 n_i \theta_i (1 - \theta_i) \\
	\implies&   \widehat{\Var} \left( \hat{\beta}_a \right)   =  \sum_{i=1}^k \left( \frac{w_i}{n_i} \right)^2 n_i \hat{\theta}_i (1 - \hat{\theta}_i) \\
	\implies&   \widehat{\Var} \left( \hat{\beta}_a \right)   =  \sum_{i=1}^k \left( \frac{w_i}{n_i} \right)^2 n_i \left( \frac{X_i}{n_i} \right) \left(1 - \frac{X_i}{n_i}\right) \\
\implies&   \widehat{\Var} \left( \hat{\beta}_a \right)   =  \sum_{i=1}^k \frac{w_i^2 \cdot X_i \cdot(1 - X_i) }{n_i^3}
\end{align*}

In some simulations where \( n_i = 200 \) and \( k = 50 \), we achieve a relative error comparing the estimator to empirical variance < 1\%.
A problem with this estimator is that when \( n_i = 1 \forall i\), \( X_i \in \{0, 1 \} \forall i \). Therefore, the estimated variance is always exactly 0.

\pagebreak

If we instead assume \( X_i \sim Poisson(n_i \theta_i) \), we have:

\begin{align*}
	        &   \Var \left( \hat{\beta}_a \right)   =  \Var \left( \sum_{i=1}^k w_i \frac{X_i}{n_i}\right)\\
	\implies&   \Var \left( \hat{\beta}_a \right)   =  \sum_{i=1}^k \left( \frac{w_i}{n_i} \right)^2 \Var X_i \\
	\implies&   \Var \left( \hat{\beta}_a \right)   =  \sum_{i=1}^k \left( \frac{w_i}{n_i} \right)^2 n_i \theta_i \\
	\implies&   \widehat{\Var} \left( \hat{\beta}_a \right)   =  \sum_{i=1}^k \left( \frac{w_i}{n_i} \right)^2 n_i \hat{\theta}_i \\
	\implies&   \widehat{\Var} \left( \hat{\beta}_a \right)   =  \sum_{i=1}^k \left( \frac{w_i}{n_i} \right)^2 n_i \frac{X_i}{n_i} \\
	\implies&   \widehat{\Var} \left( \hat{\beta}_a \right)   =  \sum_{i=1}^k \left( \frac{w_i}{n_i} \right)^2 X_i
\end{align*}

I think this is what Mike was trying to arrive at in section 6.3.

Of course, \(X_i \) is not a Poisson random variable, so this estimator is also problematic.
In some simulations where \( n_i = 200 \) and \( k = 50 \) and other simulations where \( n_i = 1 \) and \( k = 8000 \), we achieve a relative error comparing the estimator to empirical variance \( \approx \) 30\%.

Thus, an alternative for  \( \widehat{\Var} \left( \hat{\beta}_a \right) \) seems like an obvious way to improve the overall estimator.

One quick idea is to use \( \frac{X_i + 1}{n_i + 2} \) for \( \hat{\theta} \) instead of \( \frac{X_i}{n_i} \) when using the Binomial assumption.
In simulation, this estimator performs much better than the Poisson assumption when \( n_i = 200 \), and a bit worse than the Poisson assumption when \( n_i = 1 \).
Additionally, this estimator performs  much better than the Binomial assumption when \( n_i = 1 \), and a bit worse than the Poisson assumption when \( n_i = 200 \).

I'm sure Mike has additional thoughts on this.
